---
title: "Practical_One Answers"
format: html
editor: visual
output: html_document 
---

## Question  1

airquality dataset displayed below:

```{r}
airquality
head(airquality)

```

Rows with missing values:

```{r}
#| echo: false
# Find rows with missing values  
missing_values <- airquality[!complete.cases(airquality), ]  
missing_values
```

The `echo: false` option disables the printing of code (only output is displayed).

## Question  2

Output and Code for mean, sd, min, max for each of temperature and ozone level, accounting for missing values

Temperature and Ozone Summary Statistics:

```{r}
mean_temp <- mean(airquality$Temp, na.rm=T)
sd_temp <- sd(airquality$Temp)
min_temp <- min(airquality$Temp)
max_temp <- max(airquality$Temp)

mean_ozone <- mean(airquality$Ozone, na.rm=T)
sd_ozone <- sd(airquality$Ozone)
min_ozone <- min(airquality$Ozone)
max_ozone <- max(airquality$Ozone)


```

Output of summary statistics for Temperature and Ozone layer:

```{r}
#display output 



```

## Question  3: Linear Regression for cars data 

code displaying calculation of beta estimates

```{r}
# Create the design matrix X (adding a column of ones for the intercept)  
X <- cbind(1, cars$speed)

# Create the response variable Y  
Y <- cars$dist  

# Calculate the beta estimates using the formula  beta_hat <- solve(t(X) %*% X) %*% (t(X) %*% Y)  

# Display the results  
print("The beta estiamtes are:", beta_hat) 
```

## Question  4: Linear Regression for cars data 

```{r}
# Fit the linear regression model using lm()  
lm_model <- lm(dist ~ speed, data = cars)  

# Get the coefficients from the lm model  
lm_coefficients <- coefficients(lm_model) 

#Compare beta 

```
