HEAD
---
title: "Question2"
format: html
editor: visual
---

## Question 2: Find mean, sd,min,max for Temperature and Ozone Level

Output and Code for mean, sd, min, max for each of temperature and ozone level, accounting for missing values

Temperature and Ozone Summary Statistics:

```{r}
mean_temp <- round(mean(airquality$Temp, na.rm=T),2)
sd_temp <- round(sd(airquality$Temp, na.rm=T),2)
min_temp <- min(airquality$Temp)
max_temp <- max(airquality$Temp)

mean_ozone <- round(mean(airquality$Ozone, na.rm=T),2)
sd_ozone <- round(sd(airquality$Ozone, na.rm=T),2)
min_ozone <- min(airquality$Ozone)
max_ozone <- max(airquality$Ozone)


```

1.  Output of summary statistics for Temperature and Ozone layer:

```{r}
#| echo: false
#display output 
# Print summary statistics for Temperature  
print(paste("Temperature - Mean:", mean_temp))
print(paste("Temperature - SD:", sd_temp))  
print(paste("Temperature - Min:", min_temp))  
print(paste("Temperature - Max:", max_temp))  

print(paste("Ozone - Mean:", mean_ozone))  
print(paste("Ozone - SD:", sd_ozone))  
print(paste("Ozone - Min:", min_ozone))  
print(paste("Ozone - Max:", max_ozone))   



```

## Question 3: Linear Regression for cars data

code displaying calculation of beta_hat estimates

```{r}
# Create the design matrix X (adding a column of ones for the intercept)  
X <- cbind(1, cars$speed)

# Create the response variable Y  
Y <- cars$dist  

# Calculate the beta estimates using the  beta_hat formula 
beta_hat <- solve(t(X) %*% X) %*% (t(X) %*% Y)
beta_hat

```

```{r}
#| echo: false
# Display the results  
cat("The beta estimates for B0 and B1 respectively are:", beta_hat, "\n") 
```

The `echo: false` option disables the printing of code (only output is displayed).

## Question 4: Linear Regression for cars data

Check that the beta coefficients we obtained from the b_hat matrix is the same when fitting the linear regression model using lm() in R.

```{r}
# Fit the linear regression model using lm()  
lm_model <- lm(dist ~ speed, data = cars)  

# Get the coefficients from the lm model  
lm_coefficients <- coefficients(lm_model) 
lm_coefficients

#logical compare output 


```

---
title: "Question2"
format: html
editor: visual
---

## Question 2: Find mean, sd,min,max for Temperature and Ozone Level

Output and Code for mean, sd, min, max for each of temperature and ozone level, accounting for missing values

Temperature and Ozone Summary Statistics:

```{r}
mean_temp <- round(mean(airquality$Temp, na.rm=T),2)
sd_temp <- round(sd(airquality$Temp, na.rm=T),2)
min_temp <- min(airquality$Temp)
max_temp <- max(airquality$Temp)

mean_ozone <- round(mean(airquality$Ozone, na.rm=T),2)
sd_ozone <- round(sd(airquality$Ozone, na.rm=T),2)
min_ozone <- min(airquality$Ozone)
max_ozone <- max(airquality$Ozone)


```

1.  Output of summary statistics for Temperature and Ozone layer:

```{r}
#| echo: false
#display output 
# Print summary statistics for Temperature  
print(paste("Temperature - Mean:", mean_temp))
print(paste("Temperature - SD:", sd_temp))  
print(paste("Temperature - Min:", min_temp))  
print(paste("Temperature - Max:", max_temp))  

print(paste("Ozone - Mean:", mean_ozone))  
print(paste("Ozone - SD:", sd_ozone))  
print(paste("Ozone - Min:", min_ozone))  
print(paste("Ozone - Max:", max_ozone))   



```

## Question 3: Linear Regression for cars data

code displaying calculation of beta_hat estimates

```{r}
# Create the design matrix X (adding a column of ones for the intercept)  
X <- cbind(1, cars$speed)

# Create the response variable Y  
Y <- cars$dist  

# Calculate the beta estimates using the  beta_hat formula 
beta_hat <- solve(t(X) %*% X) %*% (t(X) %*% Y)
beta_hat

```

```{r}
#| echo: false
# Display the results  
cat("The beta estimates for B0 and B1 respectively are:", beta_hat, "\n") 
```

The `echo: false` option disables the printing of code (only output is displayed).

## Question 4: Linear Regression for cars data

Check that the beta coefficients we obtained from the b_hat matrix is the same when fitting the linear regression model using lm() in R.

```{r}
# Fit the linear regression model using lm()  
lm_model <- lm(dist ~ speed, data = cars)  

# Get the coefficients from the lm model  
lm_coefficients <- coefficients(lm_model) 
lm_coefficients

#logical compare output


```

